Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-25 ms.tex
finished first pass

We 
%mm also 
demonstrate
%mm
   for the first time 
that simple prescriptions 
%mm which treat stellar radiation feedback locally do not fully reproduce the same
%evolution as our fiducial model. 
    of local stellar radiation feedback fail to reproduce the evolution of our fiducial 
    model.
Our simulation with radiation localized to 20~pc around each star particle does effectively regulate star formation on short time scales, predominately by quickly destroying cold, dense gas around young, hot stars. However, this model does not drive the significant outflows seen in our fiducial simulation. Long-range ionizing radiation is important for carving channels allowing the release of significant amounts mass and metals from SNe. Our simulation with localized radiation feedback retains metals at a significantly higher fraction than expected observationally for low mass dwarf galaxies.

Finally, we note that we have performed this experiment on only one possible type of galaxy. Its low virial temperature ($\sim10^{4}$~K) makes this galaxy particularly sensitive to the effects of stellar feedback and ionizing radiation in particular. Examining the role of long-range, diffuse stellar ionizing radiation on star formation and galactic winds in more massive galaxies is an important avenue of future research.

>>>>

We 
%mm also 
demonstrate
%mm
   for the first time 
that simple prescriptions 
%mm which treat stellar radiation feedback locally do not fully reproduce the same
%evolution as our fiducial model. 
    of local stellar radiation feedback fail to reproduce the evolution of our fiducial 
    model.
Our simulation with radiation localized to 20~pc around each star particle does effectively regulate star formation on short time scales, predominately by quickly destroying cold, dense gas around young, hot stars. However, this model does not drive the significant outflows seen in our fiducial simulation. Long-range ionizing radiation is important for carving channels allowing the release of significant amounts mass and metals from SNe. Our simulation with localized radiation feedback retains a significantly higher fraction of metals than expected observationally for low mass dwarf galaxies.  
%mm
    {\bf [This point needs to be supported by a paragraph with references in the discussion.]}

Finally, we note that we have performed this experiment on only one possible type of galaxy. Its low virial temperature ($\sim10^{4}$~K) makes this galaxy particularly sensitive to the effects of stellar feedback, and ionizing radiation in particular. Examining the role of long-range, diffuse stellar ionizing radiation on star formation and galactic winds in more massive galaxies is an important avenue of future research.
